---
title: "An Introduction to the 'mstcar' Package"
author: "David DeLara"
date: "09/23/21"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{An Introduction to the 'mstcar' Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(comment = "#>", collapse = TRUE)
```

The MSTCAR package is designed to make the implementation of MSTCAR models both quick and accessible to end-users who may not have experience with Bayesian statistics or spatial analysis.

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side.

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes[^1], and tables, e.g. using `knitr::kable()`.

[^1]: A footnote here.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up \[code\] safety for \[code\] speed deserves neither." ([via](https://twitter.com/hadleywickham/status/504368538874703872))
